This is a title

### 2021-05-13 manuscript/ms.tex
writes draft simulation setup section

%%%% Custom commands
\newcommand{\gradrad}{\ensuremath{\nabla_{\rm{rad}}}}
\newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
\newcommand{\Fbot}{\ensuremath{F_{\rm{bot}}}}
\newcommand{\Ftot}{\ensuremath{F_{\rm{tot}}}}
\newcommand{\Frad}{\ensuremath{F_{\rm{rad}}}}
\newcommand{\Fconv}{\ensuremath{F_{\rm{conv}}}}
\newcommand{\Fcz}{\ensuremath{F_{\rm{cz}}}}
\newcommand{\mP}{\ensuremath{\mathcal{P}}}
\newcommand{\dP}{\ensuremath{\delta_{\rm{p}}}}
\newcommand{\Lcz}{\ensuremath{L_{\rm{cz}}}}
\newcommand{\mR}{\ensuremath{\mathcal{R}}}
\newcommand{\mS}{\ensuremath{\mathcal{S}}}
\newcommand\Pran{\ensuremath{\mathrm{Pr}}}

\newcommand{\pd}[1]{\partial_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\M}[1]{\mathbf{#1}}
\renewcommand{\dot}{\vec{\cdot}}
\newcommand{\grad}{\vec{\nabla}}
\newcommand{\cross}{\vec{\times}}
\newcommand{\laplacian}{\nabla^2}

@@

\subsection{Case I: Discontinuous radiative conductivity}
We first consider a radiative conductivity $k(z)$ which is discontinuous, with a value of $k_{\rm{CZ}}$ in the convection zone and larger value $k_{\rm{RZ}}$ in the PZ and radiative zone (RZ).
The values of $k$ are chosen so that the convective flux follows
\begin{equation}
\Fconv(z) = \begin{cases}
\Fcz			&	z \leq \Lcz,\\
-\mP_D^{-1} \Fcz & 	z > \Lcz 
\end{cases}.
\end{equation}
Here, $\mP_D^{-1}$ is the ``penetration parameter'' (subscript D for discontinuous case).
Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = \Lcz$ and the penetration zone from $z = \Lcz$ to $z = \Lcz + \dP$,
\begin{equation}
\frac{\dP}{\Lcz} = \mP_D
\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}.
\label{eqn:discontinuous_prediction}
\end{equation}
We then see that the size of the penetration region is linearly proportional to $\mP_D$ and is a function of the horizontal structure of the convective dynamics in the PZ and the CZ.
This makes sense; As $\mP_D$ grows, the magnitude of $\Fconv$ in the PZ shrinks, and so too does the breaking force of buoyancy.

\subsection{Case II: Piecewise linear radiative conductivity}
We next assume that $k(z)$ is not discontinuous at the CZ-PZ boundary, but that its derivative may be.
As a result, the convective flux in the vicinity of the boundary takes the form
\begin{equation}
\Fconv(z) = 
\begin{cases}
(\partial_z k)_{\rm{cz}}\gradad (\Lcz - z) & z \leq \Lcz \\
-\mP_L^{-1}(\partial_z k)_{\rm{cz}}\gradad (z - \Lcz) & z > \Lcz
\end{cases},
\end{equation}
where we assume that $(\partial_z \Frad)_{\rm{cz}} =  (\partial_z k)_{\rm{cz}}\gradad$ is a constant.
Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux, we retrieve
\begin{equation}
\frac{\dP}{\Lcz} = \sqrt{\mP_L
\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}},
\label{eqn:linear_prediction}
\end{equation}
which is identical to the prediction of \citet{zahn1991} when we take $\mP_L = 1$.

\section{Simulation Details}
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u} \\
&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q
\end{align}

@@

\section{Accelerated Evolution}

\section{Table of simulation parameters}

>>>>

%%%% Custom commands
\newcommand{\gradrad}{\ensuremath{\nabla_{\rm{rad}}}}
\newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
\newcommand{\Fbot}{\ensuremath{F_{\rm{bot}}}}
\newcommand{\Ftot}{\ensuremath{F_{\rm{tot}}}}
\newcommand{\Frad}{\ensuremath{F_{\rm{rad}}}}
\newcommand{\Fconv}{\ensuremath{F_{\rm{conv}}}}
\newcommand{\Fcz}{\ensuremath{F_{\rm{cz}}}}
\newcommand{\mP}{\ensuremath{\mathcal{P}}}
\newcommand{\dP}{\ensuremath{\delta_{\rm{p}}}}
\newcommand{\Lcz}{\ensuremath{L_{\rm{cz}}}}
\newcommand{\mR}{\ensuremath{\mathcal{R}}}
\newcommand{\mS}{\ensuremath{\mathcal{S}}}
\newcommand\Pran{\ensuremath{\mathrm{Pr}}}
\newcommand{\brunt}{Brunt-V\"{a}is\"{a}l\"{a}}

\newcommand{\angles}[1]{\langle #1 \rangle}
\newcommand{\pd}[1]{\partial_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\M}[1]{\mathbf{#1}}
\renewcommand{\dot}{\vec{\cdot}}
\newcommand{\grad}{\vec{\nabla}}
\newcommand{\cross}{\vec{\times}}
\newcommand{\laplacian}{\nabla^2}

@@

\subsection{Case I: Discontinuous radiative conductivity}
\label{sec:discontinuous_theory}
We first consider a radiative conductivity $k(z)$ which is discontinuous, with a value of $k_{\rm{CZ}}$ in the convection zone and larger value $k_{\rm{RZ}}$ in the PZ and radiative zone (RZ).
The values of $k$ are chosen so that the convective flux follows
\begin{equation}
\Fconv(z) = \begin{cases}
\Fcz			&	z \leq \Lcz,\\
-\mP_D^{-1} \Fcz & 	z > \Lcz 
\end{cases}.
\end{equation}
Here, $\mP_D^{-1}$ is the ``penetration parameter'' (subscript D for discontinuous case).
Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = \Lcz$ and the penetration zone from $z = \Lcz$ to $z = \Lcz + \dP$,
\begin{equation}
\frac{\dP}{\Lcz} = \mP_D
\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}.
\label{eqn:discontinuous_prediction}
\end{equation}
We then see that the size of the penetration region is linearly proportional to $\mP_D$ and is a function of the horizontal structure of the convective dynamics in the PZ and the CZ.
This makes sense; As $\mP_D$ grows, the magnitude of $\Fconv$ in the PZ shrinks, and so too does the breaking force of buoyancy.

\subsection{Case II: Piecewise linear radiative conductivity}
\label{sec:linear_theory}
We next assume that $k(z)$ is not discontinuous at the CZ-PZ boundary, but that its derivative may be.
As a result, the convective flux in the vicinity of the boundary takes the form
\begin{equation}
\Fconv(z) = 
\begin{cases}
(\partial_z k)_{\rm{cz}}\gradad (\Lcz - z) & z \leq \Lcz \\
-\mP_L^{-1}(\partial_z k)_{\rm{cz}}\gradad (z - \Lcz) & z > \Lcz
\end{cases},
\end{equation}
where we assume that $(\partial_z \Frad)_{\rm{cz}} =  (\partial_z k)_{\rm{cz}}\gradad$ is a constant.
Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux, we retrieve
\begin{equation}
\frac{\dP}{\Lcz} = \sqrt{\mP_L
\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}},
\label{eqn:linear_prediction}
\end{equation}
which is identical to the prediction of \citet{zahn1991} when we take $\mP_L = 1$.
In this work, we will test the predictions of Eqns.~\ref{eqn:linear_prediction} and \ref{eqn:discontinuous_prediction}.
Our aim is to see if the predicted scalings with $\mP$ are realized in direct numerical simulations, and to measure preliminary values for $\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}$ in local simulations.

\section{Simulation Details}
We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the convection zone, the timescale of freefall across that convection zone, and the temperature scale of the internal heating over that freefall time,
\begin{equation}
\begin{split}
&T^* = (\Delta T)T = Q_0 \tau T,\qquad
\partial_{t^*} = \tau^{-1}\partial_t = \left(\frac{\alpha g Q_0}{\Lcz}\right)^{1/3} \partial_t,\qquad
\grad^* = \Lcz^{-1} \grad,\qquad
\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(\alpha g Q_0 \Lcz^2\right)^{1/3}\vec{u},
\\
&k^* = (\Lcz^2 \tau^{-1})k,\qquad
Q^* = Q_0 Q,\qquad
\mR = \frac{u_{\rm{ff}} \Lcz}{\nu},\qquad
\Pran = \frac{\nu}{\chi}.
\end{split}
\end{equation}
Here, quantities with $*$ (e.g., $T^*$) refer to the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}, and going forward quantities without these (e.g., $T$) will be dimensionless.
The equations of motion are therefore
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:nondim_incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u}
\label{eqn:nondim_momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q.
\label{eqn:nondim_temperature}
\end{align}
We construct a domain in the range $z \in [0, L_z]$ where in this work we choose $L_z \geq 2$ so that the domain contains at least two convection zone length scales according to the Schwarzschild criterion.
We decompose the temperature field into a background and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
For boundary conditions, we impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
We also impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).

We impose an order unity internal heating which spans one fifth of the convection zone,
\begin{equation}
Q = \begin{cases}
0		& z < 0.1\,\,\rm{or}\,\,z\geq 0.1 + \delta_H,\\
|Q_{\rm{mag}}|		& 0.1 \leq z \leq 0.1 + \delta_H
\end{cases}.
\end{equation}
The integrated value of the flux through the system from the heating is therefore $F_H(z > 0.1 + \delta_H) = \int_0^z Q_{\rm{mag}} dz = Q_{\rm{mag}}\delta_H$.
Throughout this work we choose $Q_{\rm{mag}} = 1$ and $\delta_H = 0.2$ so $F_H = 0.2$.
We offset this heating from the bottom boundary to $z = 0.1$ to avoid heating within the bottom impenetrable boundary layer where velocities go to zero and $k$ is small; this prevents strong temperature gradients from establishing there.
We assume that the (adiabatic) temperature gradient at the bottom boundary carries some flux, $\Fbot = \zeta F_H$ and we choose $\zeta = 10^{-3}$ so that most of the flux in the convection zone is carried by the convection.

In our equations, we expect the volume-average convective velocities to depend on the magnitude of the heating, $\angles{\vec{u}} \approx Q_{\rm{mag}}^{1/2} \approx 1$, so the characteristic convective frequency $f_{\rm{conv}} \approx \angles{\vec{u}} \Lcz \approx 1$.
We want to allow the stiffness of the radiative-convective interface to be a control parameter.
The stiffness is defined,
\begin{equation}
\mS \equiv \frac{N^2}{f_{\rm{conv}}} \approx N^2,
\end{equation}
where $N^2$ is the \brunt$\,$frequency in the radiative zone.
In our nondimensionalization, $N^2 = \gradad - \gradrad$ where $\gradrad = \Ftot/k$, so by choosing a value of the stiffness we set the magnitude of the background temperature gradient, $T_0$ which in turn sets the value of $k$ in the radiative zone.

The crucial place in which our model differs from that of prior work is that we define a ``penetration parameter,'' $\mP$, which determines the size of the convective penetration region.
We define
\begin{equation}
\mP = -\frac{\Fconv|_{\rm{CZ}}}{\Fconv|_{PZ}},
\end{equation}
where $\Fconv|_{PZ}$ is the negative convective flux carried in a perfectly adiabatic convective penetration region.
We construct our experiments so that $\mP$ and $\mS$ can be varied separately.
We suspect that many past experiments have implicitly set $\mP \approx \mS^{-1}$.

Aside form $\mS$ and $\mP$, the two remaining control parameters that control our experiments determine the degree of turbulence.
The value of $\mR$ roughly corresponds to the value of the peak Reynolds number measured in the simulations, and we set the ratio of the diffusivities $\Pran = 0.5$ throughout this work.
Astrophysical convection is in the limit of $\Pran \ll 1$; we choose a modest value of $\Pran$ which slightly separates the scales between thermal and viscous structures while still allowing us to achieve convection with large Reynolds and P\'{e}clet numbers.

\subsection{Case I: Discontinuous radiative conductivity}
Most of the simulations in this paper study simulations with a discontinuous radiative conductivity,
\begin{equation}
k_D(z) = \begin{cases}
k_{\rm{CZ}}	&	z < 1 \\
k_{\rm{RZ}} &	z \geq 1
\end{cases}.
\end{equation}
Leaving $\mS$ and $\mP_D$ as free parameters and requiring that the adiabatic gradient can carry the $\Fbot$ at $z = 0$ and that the radiative gradient can carry the flux for $z \geq 1$ specifies this system fully,
\begin{equation}
k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\qquad
k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \zeta + \mP_D^{-1}},\qquad
\gradad = Q_{\rm{mag}}\mS\mP_D(1 + \zeta + \mP_D^{-1}),\qquad
\gradrad = \gradad - Q_{\rm{mag}}\mS.
\end{equation}

We study three sweeps through the ($\mP_D$, $\mS$, $\mR$) parameter space in this paper (one in which we vary each parameter while holding the other parameters constant).
We use ``Reference values'' of $\mP_D = 4$, $\mS = 10^3$, and $\mR = 400$; all of our parameter space sweeps pass through this point in the three-dimensional parameter space.
As in section \ref{sec:discontinuous_theory}, we expect $\delta_p \propto \mP_D$.

\subsection{Case II: Piecewise linear radiative conductivity}
We additionally study a select few simulations where the radiative conductivity's gradient is piecewise discontinuous,
\begin{equation}
\partial_z k = \partial_z k_0
\begin{cases}
1	&	z < 1 \\
\mP_L^{-1} &	z \geq 1
\end{cases}
\end{equation}
Since $k$ varies with height, the value of $\mS$ and $\mP$ also vary with height; we specify their values at $z = 2$.
by this choice, we require
\begin{equation}
\partial_z k_0 = \frac{\delta_H}{\Lcz \mS \xi},\qquad
k_b = \frac{\delta_H\zeta}{\mS\xi},\qquad
\gradad = Q \mS \xi,
\end{equation}
where $\xi \equiv 1 + \mP_L(1 + \zeta)$.
In these simulations, we hold $\mS = 10^3$ and $\mR = 800$ while varying $\mP_L$.
As in section \ref{sec:linear_theory}, we expect $\delta_p \propto \mP_L^{1/2}$.

\subsection{Numerics}
We time-evolve equations \ref{eqn:nondim_incompressible}-\ref{eqn:nondim_temperature} using the Dedalus pseudospectral solver \citep{burns_etal_2020}\footnote{we use X version} using timestepper RK443 [CITE].
All fields are represented as spectral expansions of $n_z$ Chebyshev coefficients in the vertical ($z$) direction and as ($n_x$,$n_y$) Fourier coefficients in the horizontal ($x$,$y$) directions; our domains are therefore horizontally periodic.
The aspect ratio of our domains is two so that $x \in [0, L_x]$ and $y \in [0, L_y]$ with $L_x = L_y = 2 L_z$.
To start our simulations, we add random noise temperature perturbations with a magnitude of $10^{-3}$ to a background temperature profile $\overline{T}$; we discuss the choice of $\overline{T}$ in appendix \ref{app:accelerated_evolution}.
We produce the figures in this paper using matplotlib [CITE].
All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repo, found at [CITE].

@@

\section{Accelerated Evolution}
\label{app:accelerated_evolution}

\section{Table of simulation parameters}
\label{app:simulation_table}
